A Global Sensitivity Analysis of Wind Turbine Aeroelastic Models

### 2019-09-25 Paper/article.tex
generalized the sensitivity analysis workflow

\documentclass[review]{elsarticle}
\usepackage{lineno,hyperref}
\modulolinenumbers[5]
\journal{ }
\usepackage{microtype}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[a4paper, total={6.2in, 9in}]{geometry}
\usepackage[a4paper]{geometry}
\renewcommand{\baselinestretch}{1.2} 
\usepackage{color}
\usepackage[x11names]{xcolor}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{tabularx,ragged2e,booktabs,caption}
\renewcommand{\figurename}{{Figure}}
\usepackage[labelfont=bf]{caption}
\usepackage[font=footnotesize]{caption}
\usepackage{amssymb,latexsym}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{tikz}
\usepackage{array}
\usepackage{mathtools}
\usepackage{relsize}
\usepackage[T1]{fontenc}
\usepackage{cases}
\usepackage{amsthm}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage[toc,page]{appendix}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\newtheorem{theorem}{Theorem}
\newtheorem{remark}{Remark}[section]
\numberwithin{equation}{section}
\usepackage{tabularx,ragged2e,booktabs,caption}
\newcommand{\footremember}[2]{%
    \footnote{#2}
    \newcounter{#1}
    \setcounter{#1}{\value{footnote}}%
}
\newcommand{\footrecall}[1]{%
    \footnotemark[\value{#1}]%
}
\usepackage[toc]{appendix}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
\newcommand{\lnorm}{\left|\left|}
\newcommand{\rnorm}{\right|\right|}
\newcommand{\Ld}{L^2(\mathcal{D})}
\newcommand{\Lomtd}{L^2(\Omega;\mathcal{T};\mathcal{D})}
%\newcommand{\Lomd}{L^2(\Omega;L^2(\mathcal{D}))}
\newcommand{\Lomd}{L^2(\Omega,\mathcal{D})}
\newcommand{\myreferences}{../Bibliography/references}
\bibliographystyle{elsarticle-num}
\numberwithin{equation}{section}
\usepackage{tabularx,ragged2e,booktabs,caption}
\graphicspath{{./images/}}
\usepackage[toc]{appendix}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
\bibliographystyle{elsarticle-num}
\usepackage{stix2}
\usepackage{pgfplots}
\usepackage{appendix}
\usepackage[labelfont=bf]{caption}
\pgfplotsset{compat=newest}
\pagestyle{myheadings}
%%%%%%%%%%%%%%%%%%%%%%%
\title{A Global Sensitivity Analysis of Wind Turbine Aeroelastic Models}
\begin{document}
\begin{frontmatter}
%\address[cwi]{CWI - Centrum Wiskunde \& Informatica, Amsterdam, The Netherlands}
%\address[aero]{Faculty of Aerospace Engineering, Delft University of Technology, Delft, The Netherlands.}
%\author[cwi,aero]{Prashant~Kumar}
\author[]{Prashant~Kumar}
\ead{pkumar@cwi.nl}
\begin{abstract}
Wind turbines are a complex multi-physics systems. As the performance and the life span of a turbine is highly dependent on  manufacturing, meteorological and operational factors, it is very important to quantify the impact of each of these parameter in the output of interest.  
\end{abstract}
\begin{keyword}
Wind energy, global sensitivity analysis, UQ, aeroelastic models 
\end{keyword}
\end{frontmatter}
\linenumbers
\section{Introduction}
\section{Aeroelastic models}
\subsection{BEM models}
\subsection{Input parameters of aeroelastic models}
\section{Global sensitivity analysis}
The main objective of sensitivity analysis is to quantify the relative significance of individual inputs (or in combination) and how variations in input values affects the output of interest. In engineering, sensitivity analysis can be employed for a number of reasons: to determine the stability and robustness of a computational model with respect to input parameters, for simplification of stochastic models by fixing the insensitive parameters, and to guide data acquisition campaigns and experimental design to refine the data on sensitive parameters.

>>>>

\documentclass[review]{elsarticle}
\usepackage{lineno,hyperref}
\modulolinenumbers[5]
\journal{ }
\usepackage{microtype}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[a4paper, total={6.2in, 9in}]{geometry}
\usepackage[a4paper]{geometry}
\renewcommand{\baselinestretch}{1.2} 
\usepackage{color}
\usepackage[x11names]{xcolor}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{tabularx,ragged2e,booktabs,caption}
\renewcommand{\figurename}{{Figure}}
\usepackage[labelfont=bf]{caption}
\usepackage[font=footnotesize]{caption}
\usepackage{amssymb,latexsym}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{tikz}
\usepackage{array}
\usepackage{mathtools}
\usepackage{relsize}
\usepackage[T1]{fontenc}
\usepackage{cases}
\usepackage{amsthm}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage[toc,page]{appendix}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\newtheorem{theorem}{Theorem}
\newtheorem{remark}{Remark}[section]
\numberwithin{equation}{section}
\usepackage{tabularx,ragged2e,booktabs,caption}
\newcommand{\footremember}[2]{%
    \footnote{#2}
    \newcounter{#1}
    \setcounter{#1}{\value{footnote}}%
}
\newcommand{\footrecall}[1]{%
    \footnotemark[\value{#1}]%
}
\usepackage[toc]{appendix}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
\newcommand{\lnorm}{\left|\left|}
\newcommand{\rnorm}{\right|\right|}
\newcommand{\Ld}{L^2(\mathcal{D})}
\newcommand{\Lomtd}{L^2(\Omega;\mathcal{T};\mathcal{D})}
%\newcommand{\Lomd}{L^2(\Omega;L^2(\mathcal{D}))}
\newcommand{\Lomd}{L^2(\Omega,\mathcal{D})}
\newcommand{\myreferences}{../Bibliography/references}
\bibliographystyle{elsarticle-num}
\numberwithin{equation}{section}
\usepackage{tabularx,ragged2e,booktabs,caption}
\graphicspath{{./images/}}
\usepackage[toc]{appendix}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
\bibliographystyle{elsarticle-num}
\usepackage{stix2}
\usepackage{pgfplots}
\usepackage{appendix}
\usepackage[labelfont=bf]{caption}
\pgfplotsset{compat=newest}
\pagestyle{myheadings}
%%%%%%%%%%%%%%%%%%%%%%%
\title{A Global Sensitivity Analysis of Wind Turbine Aeroelastic Models}
\begin{document}
\begin{frontmatter}
%\address[cwi]{CWI - Centrum Wiskunde \& Informatica, Amsterdam, The Netherlands}
%\address[aero]{Faculty of Aerospace Engineering, Delft University of Technology, Delft, The Netherlands.}
%\author[cwi,aero]{Prashant~Kumar}
\author[]{Prashant~Kumar}
\ead{pkumar@cwi.nl}
\begin{abstract}
Wind turbines are a complex multi-physics systems. As the performance and the life span of a turbine is highly dependent on  manufacturing, meteorological and operational factors, it is very important to quantify the impact of each of these parameter in the output of interest.  
\end{abstract}
\begin{keyword}
Global sensitivity analysis, UQ, Sobol indices, aeroelastic models
\end{keyword}
\end{frontmatter}
\linenumbers
\section{Introduction}
Aeroelastic models such as the Blade Element Momentum (BEM) models \cite{HandBook} play a critical role in the design, development and optimization of modern wind turbines. In particular, BEM models are employed to predict turbine response such as the structural loads and power outputs. A number of parameters describing meteorological and operational conditions as well as manufacturing specifications are needed as input to simulate BEM models. In this work, we seek to quantify the sensitivities of these input parameters for different turbine responses.
\section{Aeroelastic models}
\subsection{BEM models}
\subsection{Input parameters of aeroelastic models}
\section{Global sensitivity analysis}
The main objective of sensitivity analysis is to quantify the relative significance of individual inputs (or in combination) and how variations in input values affects the output of interest. In engineering, sensitivity analysis can be employed for a number of reasons: to determine the stability and robustness of a computational model with respect to input parameters, for simplification of stochastic models by fixing the insensitive parameters, and to guide data acquisition campaigns and experimental design to refine the data on sensitive parameters.
